---
title: "Counties of Occurrence of ESA-listed Species"
author: "Defenders of Wildlife"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(DT)
library(RPostgreSQL)
library(secret)

con <- dbConnect(
  dbDriver("PostgreSQL"),
  dbname = "postgres",
  user = ESC_DB_USR,
  password = get_secret(ESC_DB_PW, key = priv_key, vault),
  host = ESC_DB
)

cnt <- dbSendQuery(con, "select * from esa_county_occurrences") %>% 
  dbFetch() %>%
  select(-state_abbreviation)

names(cnt) <- c(
  "Common Name",
  "Scientific Name",
  "URL",
  "County Name",
  "FIPS",
  "State"
)

cnt <- select(cnt, c(1:4, 6, 5))
```

<hr style='width=75%'>

This table provides basic search and filtering of the counties of occurrence for 
ESA-listed species based on the data available through the [U.S. Fish and Wildlife Service's](http://www.fws.gov) 
[ECOS](https://ecos.fws.gov) website. 

Type searches into the filter box in the 
top-right to filter across all columns, or use the search boxes at the top of 
each column for column-specific filtering. Click the arrows at the top of columns
to sort.

<hr style='width=75%'>

```{r tab, echo = FALSE, warning = FALSE}
DT::renderDataTable(
  cnt,
  server = TRUE,
  filter = "top",
  escape = FALSE,
  extensions = "Buttons",
  options = list(
    pageLength = 25,
    lengthMenu = c(10, 25, 50, 100),
    dom = 'Bfrtip',
    buttons = c('copy', 'excel', 'print')
  )
)

htmltools::tags$br()
htmltools::tags$br()
htmltools::tags$hr(style = "width:75%")
```

